---
title: "p8105_hw1_tl3196"
author: "Tianshu Liu"
date: "2022-09-17"
output: html_document
---

# Problem 1

```{r install_penguins, eval=FALSE}
install.packages("palmerpenguins")
```


```{r penguins, echo = TRUE}
data("penguins", package = "palmerpenguins")
```

```{r show_penguins, echo = FALSE}
penguins
```

The 'penguins' dataset is a tibble of ``r nrow(penguins)` × `r ncol(penguins)``.

The variables include ``r colnames(penguins)``.

-   Species - `r class(penguins$species)`, the species of the penguins.

-   Island - `r class(penguins$island)`, the island the penguin lives on.

-   Bill_length_mm - `r class(penguins$bill_length_mm)`, the length of penguin's bill in mm.

-   Bill_depth_mm - `r class(penguins$bill_depth_mm)`, the depth of penguin's bill in mm.

-   Flipper_length_mm - `r class(penguins$flipper_length_mm)`, the length of penguin's flipper in mm. The mean length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.

-   Body_mass_g - `r class(penguins$body_mass_g)`, penguin's body mass in gram.

-   Sex - `r class(penguins$sex)`, penguin's sex.

-   Year - `r class(penguins$year)`, the year that the penguin's egg was found.

```{r scatterplot, message=FALSE, warning=FALSE}
library(tidyverse)
ggplot(penguins, aes(y = flipper_length_mm, x = bill_length_mm, color = species)) + geom_point()
ggsave("scatterplot.png")
```

# Problem 2

```{r generate_df}
data_type_df =
  tibble(
  random_norm = rnorm(n = 10, mean = 0, sd = 1),
  logical = random_norm > 0, 
  character = c("A", "B", "C", "D", "E", "F", "G", "H", "I", "J"),
  factor = factor(sample(1:3, 10, replace = TRUE), levels = c(1, 2, 3), labels =c ("bad", "okay", "good"))
)

```

```{r show_df, echo=FALSE}
data_type_df
```

The mean of each col is:

-  random_norm : ``r mean(pull(data_type_df, random_norm))``
-  logical : ``r mean(pull(data_type_df, logical))``
-  character : ``r mean(pull(data_type_df, character))``
-  factor : ``r mean(pull(data_type_df, factor))``

Conclusion: when calculating mean, it works for numeric and logical variables, not for character and factor vectors.

After using `as.numeric()` function:

-  random_norm : ``r mean(as.numeric(pull(data_type_df, random_norm)))``
-  logical : ``r mean(as.numeric(pull(data_type_df, logical)))``
-  character : ``r mean(as.numeric(pull(data_type_df, character)))``
-  factor : ``r mean(as.numeric(pull(data_type_df, factor)))``

Conclusion: After using `as.numeric()` function, the mean of logical variables remains the same as before, the mean of factor variables can be calculated, but the mean of character variables is still NA.

Reason: 

The `as.numeric()` function can convert the value of logical and factor variables to numeric variables which can be used to calculate means.

The `as.numeric()` function converts the value of logical variables from `TRUE /FALSE` to `0 / 1`. 
In this case, the values of input logical variables ``r pull(data_type_df, logical)`` turns out to be ``r as.numeric(pull(data_type_df, logical))``, which can be used to calculate mean ``r mean(as.numeric(pull(data_type_df, logical)))``; 

The `as.numeric()` function converts the value of factor variables to numbers based on the maps between levels and labels. 
In this case, the factor variables``r pull(data_type_df, factor)`` turns out to be ``r as.numeric(pull(data_type_df, factor))``, which can also be calculated for the mean;

The character variables``r pull(data_type_df, character)`` turns out to be ``r as.numeric(pull(data_type_df, character))``, which are all NAs so that the mean cannot be calculated.