---
title: "p8105_hw1_tl3196"
author: "Tianshu Liu"
date: "2022-09-17"
output: html_document
---

# Problem 1

```{r penguins, echo = TRUE}
data("penguins", package = "palmerpenguins")

```

```{r show_penguins, echo = FALSE}
penguins
```

The 'penguins' dataset is a tibble of `r nrow(penguins)` × `r ncol(penguins)`.

The variables include `r colnames(penguins)`.

-   Species - factor, the species of the penguins.

-   Island - factor, the island the penguin lives on.

-   Bill_length_mm - numeric, the length of penguin's bill in mm.

-   Bill_depth_mm - numeric, the depth of penguin's bill in mm.

-   Flipper_length_mm - integer, the length of penguin's flipper in mm. The mean length is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`.

-   Body_mass_g - integer, penguin's body mass in gram.

-   Sex - factor, penguin's sex.

-   Year - integer, the year that the penguin's egg was found.

```{r scatterplot, message=FALSE, warning=FALSE}
library(tidyverse)
ggplot(penguins, aes(y = flipper_length_mm, x = bill_length_mm, color = species)) + geom_point()
ggsave("scatterplot.png")
```



Export your first scatterplot to your project directory using ggsave.
